\pdftitle

### 2018-07-27 nips_2018_author_response.tex
update text and scripts

\usepackage[shortlabels,inline]{enumitem}
\SetEnumitemKey{para}{itemindent=\parindent,leftmargin=0pt,listparindent=\parindent,parsep=0pt,itemsep=\topsep}
% \begin{asparaenum} = \begin{enumerate}[para]
% \begin{inparaenum} = \begin{enumerate*}
\setlist[enumerate,2]{label=\alph*.}
\setlist[enumerate]{leftmargin=1.5em}
\setlist[itemize]{leftmargin=1.5em}
\setlist[description]{leftmargin=\parindent}

@@

\medskip

\textbf{Reviewer 2}
\begin{enumerate}
\item We agree that the comparison with other approaches is important. But
  we believe that it's also important to carefully examine (1) the question
  we're asking, and (2) which first principles, if any, can be used to
  translate it into a mathematical problem. A lot of literature develops
  very refined -- though often ad hoc -- mathematical techniques; and yet
  it leaves us unsatisfied, with the lingering question \enquote{why were
    we doing this?}. This is the reason for our long introductory
  discussion about the problem and the first principles that can be used to
  address it.
\item Regarding the effect of correlations on the result: the original
  question is how \enquote{cooperativity} can be related to the measured
  correlations, or defined in terms of them. The method is devised to give
  one answer to this question; see the \enquote{protocol} 1--3 in the
  Introduction. The crucial point is that there is no underlying
  distribution; the point of the method is to construct it for us.
\item We agree that there are many approaches in the literature. In the
  literature we have explored we've seen very little use of the basic
  sampling formulae presented in our paper. Honestly this surprised us,
  because they're surely essential even in a very basic analysis of the data.
\end{enumerate}

\medskip

\textbf{Reviewer 3}
\begin{enumerate}
\item We also agree with Reviewer 3 that the main formulae of the paper,
  (17) and (19), probably have little experimental use today. But the point
  they make is important:
  \begin{itemize}
  \item the Reviewer says \enquote{the differences between the sample level
      and population level distribution seem minor} -- but we could not
    have known this, if we hadn't faced the whole problem and derived a
    formula showing that the difference is minor;
  \item the sample-level distribution is actually \emph{less} entropic. By
    lifting the constraints to the population level, the maximum-entropy
    principle allows us to explore even \emph{more entropic} sample
    distributions than those allowed by a direct application at the sample
    level. Thus this approach agrees with the \enquote{maximum entropy}
    spirit. -- These points should be mentioned, of course, in an amended
    version of the paper.
  \item 
  \end{itemize}
\item We agree with Reviewer 3 that the paper emphasizes some philosophical
  aspects; intentionally so. Sadly we can't make all kinds of readers
  happy; a choice of audience is necessary. As readers ourselves we
  appreciate when a paper begins by asking: \enquote{What is the question?
    is it possible to translate it into a mathematical problem? which
    principles can we use to make such translation?}. There are papers that
  develop very refined mathematical techniques but leave us unsatisfied,
  with the lingering question \enquote{why are we doing this?}. This is the
  reason why we try to emphasize these kinds of questions. But we are sure
  that part of the NIPS audience will appreciate this emphasis.

>>>>

\usepackage[shortlabels,inline]{enumitem}
\SetEnumitemKey{para}{itemindent=\parindent,leftmargin=0pt,listparindent=\parindent,parsep=0pt,itemsep=\topsep,topsep=0pt}
% \begin{asparaenum} = \begin{enumerate}[para]
% \begin{inparaenum} = \begin{enumerate*}
\setlist[enumerate,2]{label=\alph*.}
\setlist[enumerate]{leftmargin=1.5em,topsep=-1ex}
\setlist[itemize]{leftmargin=1.5em}
\setlist[description]{leftmargin=\parindent}

@@

\bigskip

\textbf{Reviewer 2}
\begin{enumerate}
\item We agree that the comparison with other approaches is important. But
  we believe that it's also important to carefully examine (1) the question
  we're asking, and (2) which first principles can be used to translate it
  into a mathematical problem. Some literature develops very refined --
  though often ad hoc -- mathematical techniques, but then leaves us
  unsatisfied, with the lingering question \enquote{why were we doing
    this?}. This is the reason for our long introductory discussion about
  the problem and the first principles that can be used to address it.
\item The firing rate likely affects the results and the quantification of
  \enquote{cooperativity}. Is this an issue? is our idea of
  \enquote{cooperativity} invariant with respect to the firing rate, or
  not? Requirements of this kind constrain the translation of cooperativity
  into a mathematical quantity. This again shows the importance of defining
  the question we're asking first.
\item Regarding correlations: the method quantifies cooperativity using the
  measured correlations; see the \enquote{protocol} 1--3 in the
  Introduction. Thus, correlations determine the result.
\item We agree that there are many approaches in the literature. In the
  literature we have explored we've seen very little use of the basic
  sampling formulae presented in our paper. Honestly this surprised us,
  because they're surely essential even in a very basic analysis of the data.
\end{enumerate}

\bigskip

\textbf{Reviewer 3}
\begin{enumerate}
\item We agree with the Reviewer that the main formulae of the paper, (17)
  and (19), probably have little \emph{experimental} use today. But the
  formulae and the analysis behind them are important exactly for the
  points raised by the Reviewer:
  \begin{itemize}
  \item \begin{minipage}[t]{0.8\linewidth} the Reviewer says \enquote{the
        differences between the sample level and population level
        distribution seem minor} -- this can be true, but we could not have
      known this, if we hadn't faced the whole problem and derived a
      formula showing that the difference is minor;
    \end{minipage}
  \item
    \begin{minipage}[t]{0.8\linewidth}
      application of the method with higher-order constrains can show more
      interesting differences between sample- and population-level
      distributions. See e.g. the plot on the right. This should be added
      in an amended version of the paper. Unfortunately there are space
      constraints.
    \end{minipage}\hspace{\fill}
    \smash{\begin{minipage}[c]{0.19\linewidth}\vspace{0pt}
      \includegraphics[width=\linewidth]{zoom_4mom.png}
    \end{minipage}}

%     % \setlength{\intextsep}{0.5ex}% with wrapfigure
%     \begin{figure}[h!]%{r}{0.4\linewidth} % with wrapfigure
%   \centering
% %\caption{***}\label{fig:comparison_a5}
% \end{figure}
  \item The population-level distribution can be more or less entropic of
    the sample-level one. is actually \emph{less} entropic. By
    lifting the constraints to the population level, the maximum-entropy
    principle allows us to explore even \emph{more entropic} sample
    distributions than those allowed by a direct application at the sample
    level. Thus this approach agrees with the \enquote{maximum entropy}
    spirit. -- These points should be mentioned, of course, in an amended
    version of the paper.
  \item 
  \end{itemize}
\item We agree with Reviewer 3 that the paper emphasizes some philosophical
  aspects; intentionally so. Sadly we can't make all kinds of readers
  happy; a choice of audience is necessary. As readers ourselves we
  appreciate when a paper begins by asking: \enquote{What is the question?
    is it possible to translate it into a mathematical problem? which
    principles can we use to make such translation?}. There are papers that
  develop very refined mathematical techniques but leave us unsatisfied,
  with the lingering question \enquote{why are we doing this?}. This is the
  reason why we try to emphasize these kinds of questions. But we are sure
  that part of the NIPS audience will appreciate this emphasis.
